Analysis and elimination of bottlenecks\\ in parallel algorithm for solving\\ global optimization problems

### 2022-10-04 2022/RSD/paper.tex
submitted to Springer

\usepackage{hyperref}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
\usepackage{color}
\renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{amsmath} 
\usepackage{multirow} 
%
\begin{document}
%
\title{Analysis and elimination of bottlenecks\\ in parallel algorithm for solving\\ global optimization problems}
%
\titlerunning{Analysis and elimination of bottlenecks in parallel algorithm}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{
Konstantin Barkalov \orcidID{0000-0001-5273-2471} \and
Ilya Lebedev \orcidID{0000-0002-8736-0652} \and
Denis Karchkov \orcidID{0000-0002-4164-5927}
}
%
\authorrunning{K. Barkalov, I. Lebedev, D. Karchkov}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Lobachevsky State University of Nizhny Novgorod, Nizhny Novgorod, Russia \\
\email{\{konstantin.barkalov,ilya.lebedev,karchkov\}@itmm.unn.ru}
}

>>>>

\usepackage{hyperref}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
\usepackage{color}
\renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{amsmath} 
\usepackage{multirow} 
\usepackage{marvosym}

%
\begin{document}
%
\title{Analysis and elimination of bottlenecks\\ in parallel algorithm for solving\\ global optimization problems}
%
\titlerunning{Analysis and elimination of bottlenecks in parallel algorithm}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{
Konstantin Barkalov$^\textrm{\Letter}$ \orcidID{0000-0001-5273-2471} \and
Ilya Lebedev \orcidID{0000-0002-8736-0652} \and
Denis Karchkov \orcidID{0000-0002-4164-5927}
}
%
\authorrunning{K. Barkalov, I. Lebedev, D. Karchkov}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Lobachevsky State University of Nizhny Novgorod, Nizhny Novgorod, Russia \\
\email{\{konstantin.barkalov,ilya.lebedev,karchkov\}@itmm.unn.ru}
}
